\cvsection{\ProjectsLabel}

\cvproject{CCCD 2026 Rocketry Program --- Director, SpaceTech Rocketry}
{Ongoing}
{
\begin{cvitems}
\item Leading two rocket development teams focused on fiberglass and carbon-fiber composite platforms.
\item Directing avionics, telemetry downlink, manufacturing, and flight-test activities.
\end{cvitems}
}

\cvproject{Experimental Rocketry Development Program --- Director, SpaceTech Rocketry}
{Ongoing}
{
\begin{cvitems}
\item Leading SpaceTech's transition from sport rocketry toward experimental rocket systems.
\item Establishing solid-propellant research, safety requirements, and development roadmaps.
\end{cvitems}
}

\cvproject{CanSat World Championship 2026 --- Fuselage Development Director}
{2026}
{
\begin{cvitems}
\item Led development of a fiberglass airframe for an autonomous CanSat competition platform.
\item Reduced projected enclosure mass by 77% compared to an equivalent aluminum design.
\item Designed structural interfaces supporting avionics, payload, and recovery integration.
\end{cvitems}
}

\cvproject{CCCD 2025 Sounding Rocket Program --- Aerodynamics \& Mechanical Design Director}
{2025}
{
\begin{cvitems}
\item Led aerodynamics and mechanical design for a fiberglass sounding rocket competition platform.
\item Designed aerodynamic surfaces, internal structures, and subsystem interfaces.
\item Validated performance through CFD, structural simulations, and materials testing.
\end{cvitems}
}

\cvproject{Ion Thruster Research Project}
{2024}
{
\begin{cvitems}
\item Developed analytical models for ion acceleration and charge transport phenomena.
\item Performed first-pass calculations of electron mass flow and plasma behavior.
\item Supported literature review and early-stage electric propulsion feasibility studies.
\end{cvitems}
}
